The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-02-01 repeater-vladata.tex
moved example intro in

\section{Introduction}
Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[DM; ][]{2007Sci...318..777L}. Their large DM implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}. Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}. However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.

>>>>

\section{Introduction}
% cut from vla slsn proposal
%In the ten years since their discovery, the study of Fast Radio Bursts (FRBs) has followed a winding road. The first recognized FRB \citep[the ''Lorimer burst'';][]{2007Sci...318..777L} presented a cosmic curiosity with profound implications. That millisecond transient had an anomalously high dispersion \citep[$DM >> DM_{\rm{Milky Way}}$;][]{2002astro.ph..7156C} that implied its source was at cosmological distances ($z\sim0.5$). At that distance, the radio bursts must have a luminosity several orders of magnitude larger than the Crab pulsar \citep{2016MNRAS.457..232C}.
%
%The FRB story took several dramatic turns with the discovery of a new kind of terrestrial interference \citep[''perytons'';][]{2011ApJ...727...18B} and another 17 FRBs by telescopes around the world \citep{2013Sci...341...53T, 2014ApJ...790..101S, 2015Natur.528..523M}. However, FRB models ranged from the profound \citep{2014A&A...562A.137F} to the trivial \citep{2014ApJ...797...70K}. The discovery of a repeating FRB by the Arecibo Observatory \citep[\frb;][]{2016Natur.531..202S} demonstrated that at least some FRBs are not cataclysmic. It also suggested that the bursts could be an energetic cousin of well-known neutron star radio transient phenomena.
%
%At this point, FRB models were poorly constrained by the single-dish telescopes that were discovering the bursts. Those observatories localized bursts to an area of tens of arcminutes, which is far too large to identify unique multiwavelength counterparts. The \emph{realfast}\footnote{See \url{http://realfast.io}.} project was designed to solve that problem by enabling large-scale interferometric surveys for FRBs with the VLA \citep{2015ApJ...807...16L}. As of January 2017, the fruits of that effort have become clear: the VLA has made the first direct localization of an FRB and uniquely associated it with a galaxy at $z=0.1973$\ \citep{2017Natur.541...58C, 2017ApJ...834L...7T}. With a cosmological distance firmly established, the initial promise of \citet{2007Sci...318..777L} is beginning to be realized.

Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[DM; ][]{2007Sci...318..777L}. Their large DM implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}. Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}. However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.
